Supplementary Materials: Probing the Deuteron at Very Large Internal Momenta

### 2020-10-03 PRL_UTILITIES_CODES/prl_plot_tests/MARKED_PRL/ms.tex
finalized supp. materials and modifications of prl text / images

simulation program, SIMC \cite{PhysRevC.64.054610}(see Supplemental Material). Additional $^{1}\mathrm{H}(e,e'p)$ data were also taken at three other kinematic settings that covered the SHMS momentum acceptance range for the deuteron and were used for spectrometer optics optimization, 

@@

originated from the same reaction vertex at the target (See Supplemental Material). \\

@@

\indent The data were radiatively corrected for each bin in ($\theta_{nq}, p_{\mathrm{r}}$) by multiplying the measured cross sections by the ratio of the calculated particle yield excluding and including radiative effects. The SIMC simulation code was used for these calculations with the Deuteron Model by Laget including FSI \cite{LAGET2005}.

@@

over the kinematic bin. The systematic uncertainties associated with the radiative and bin-centering corrections were investigated using the Laget PWIA and FSI models but negligible effects on the cross sections were found (see Supplemental Material). The experimental and theoretical reduced cross sections were extracted and are defined as follows:

@@

\indent At larger recoil momenta, where the ratio $R>1$ and increasing with $p_{\mathrm{r}}$, for $\theta_{nq}=35^{\circ}$ FSI start to dominate for

@@

%---include references that are not mentioned in the main text
%---but are included in the supplemental material
%---cite supp. material as follows:  (See Supplemental Material) after description of the topic being discussed.
%\nocite{COSY}

>>>>

simulation program, SIMC \cite{PhysRevC.64.054610} (see Supplemental Material). Additional $^{1}\mathrm{H}(e,e'p)$ data were also taken at three other kinematic settings that covered the SHMS momentum acceptance range for the deuteron and were used for spectrometer optics optimization, 

@@

originated from the same reaction vertex at the target (see Supplemental Material). \\

@@

\indent The data were radiatively corrected for each bin in ($\theta_{nq}, p_{\mathrm{r}}$) by multiplying the measured cross sections by the ratio of the calculated particle yield excluding and including radiative effects.
The SIMC simulation code was used for these calculations with the Deuteron Model by Laget including FSI \cite{LAGET2005}.

@@

over the kinematic bin. The systematic uncertainties associated with the radiative and bin-centering corrections were investigated using the Laget PWIA and FSI models but negligible effects on the cross sections were found (see Supplemental Material).
The experimental and theoretical reduced cross sections were extracted and are defined as follows:

@@

\indent At larger recoil momenta, where the ratio $R>1$ and increasing with $p_{\mathrm{r}}$, for $\theta_{nq}=35^{\circ}$ FSI start to dominate at

@@

%---include references that are not mentioned in the main text
%---but are included in the supplemental material
%---cite supp. material as follows:  (See Supplemental Material) after description of the topic being discussed.
\nocite{COSY}
\nocite{barlow2002systematic}
\nocite{barlow2017}

### 2020-10-03 PRL_UTILITIES_CODES/prl_wordcount/ms.tex
finalized supp. materials and modifications of prl text / images

\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress]{revtex4-2}  % for review and submission
\pdfoutput=1 
\usepackage{graphicx}  % needed for figures
\usepackage{ragged2e}
\usepackage{dcolumn}   % needed for some tables
\usepackage{bm}        % for math
\usepackage{amssymb}   % for math
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{float}
\usepackage{lipsum}
\hypersetup{
    colorlinks,
    linkcolor={blue!80!black},
    citecolor={blue!80!black},
    urlcolor={blue!80!black}
}
\hyphenation{ALPGEN}
\hyphenation{EVTGEN}
\hyphenation{PYTHIA}

@@

\indent The data were radiatively corrected for each bin in ($\theta_{nq}, p_{\mathrm{r}}$) by multiplying the measured cross sections by the ratio of the calculated particle yield excluding and including radiative effects.
The SIMC simulation code was used for these calculations with the Deuteron Model by Laget including FSI \cite{LAGET2005}.

@@

over the kinematic bin. The systematic uncertainties associated with the radiative and bin-centering corrections were investigated using the Laget PWIA and FSI models but negligible effects on the cross sections were found (see Supplemental Material).
The experimental and theoretical reduced cross sections were extracted and are defined as follows:
\begin{equation}
\sigma_{\mathrm{red}} \equiv \frac{\sigma_{\mathrm{exp(th)}}}{E_{\mathrm{f}}p_{\mathrm{f}}f_{\mathrm{rec}}\sigma_{\mathrm{cc1}}},
\label{eq:1}
\end{equation}

@@

\indent At larger recoil momenta, where the ratio $R>1$ and increasing with $p_{\mathrm{r}}$, for $\theta_{nq}=35^{\circ}$ FSI start to dominate at

@@

\indent We acknowledge the outstanding support of the staff of the Accelerator and Physics Divisions at Jefferson Lab
as well as the entire Hall C staff, technicians, graduate students and users who took shifts or contributed
to the equipment for the Hall C upgrade, making all four commissioning experiments possible. We would also like to
thank Misak Sargsian, J.M. Laget, Sabine Jeschonnek and J.W. Van Orden for providing the theoretical calculations as well as the useful
discussions we had on this topic. This work was supported in part by the U.S. Department of Energy (DOE), Office of Science, Office of Nuclear Physics
under grant No. DE-SC0013620 and contract DE-AC05-06OR23177, the Nuclear Regulatory Commission (NRC) Fellowship
under grant No. NRC-HQ-84-14-G-0040, the Doctoral Evidence Acquisition (DEA) Fellowship and the Natural Sciences and Engineering Research Council of Canada (NSERC).

%---include references that are not mentioned in the main text
%---but are included in the supplemental material
%---cite supp. material as follows:  (See Supplemental Material) after description of the topic being discussed.
\nocite{COSY}
\nocite{barlow2002systematic}
\nocite{barlow2017}

\bibliography{ms}
\end{document}

>>>>

\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress,nofootbib]{revtex4-2}  % for review and submission
\pdfoutput=1 
\usepackage{graphicx}  % needed for figures
\usepackage{ragged2e}
\usepackage{dcolumn}   % needed for some tables
\usepackage{bm}        % for math
\usepackage{amssymb}   % for math
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{float}
\usepackage{lipsum}
\hypersetup{
    colorlinks,
    linkcolor={blue!80!black},
    citecolor={blue!80!black},
    urlcolor={blue!80!black}
}
\hyphenation{ALPGEN}
\hyphenation{EVTGEN}
\hyphenation{PYTHIA}

@@

\indent The data were radiatively corrected for each bin in ($\theta_{nq}, p_{\mathrm{r}}$) by multiplying the measured cross sections by the ratio of the calculated particle yield excluding and including radiative effects. The SIMC simulation code was used for these calculations with the Deuteron Model by Laget including FSI \cite{LAGET2005}.

@@

over the kinematic bin. The systematic uncertainties associated with the radiative and bin-centering corrections were investigated using the Laget PWIA and FSI models but negligible effects on the cross sections were found (see Supplemental Material). The experimental and theoretical reduced cross sections were extracted and are defined as follows:
%\begin{equation}
%\sigma_{\mathrm{red}} \equiv \frac{\sigma_{\mathrm{exp(th)}}}{E_{\mathrm{f}}p_{\mathrm{f}}f_{\mathrm{rec}}\sigma_{\mathrm{cc1}}},
%\label{eq:1}
%\end{equation}

@@

\indent At larger recoil momenta, where the ratio $R>1$ and increasing with $p_{\mathrm{r}}$, for $\theta_{nq}=35^{\circ}$ FSI start to dominate for

@@

%\indent We acknowledge the outstanding support of the staff of the Accelerator and Physics Divisions at Jefferson Lab
%as well as the entire Hall C staff, technicians, graduate students and users who took shifts or contributed
%to the equipment for the Hall C upgrade, making all four commissioning experiments possible. We would also like to
%thank Misak Sargsian, J.M. Laget, Sabine Jeschonnek and J.W. Van Orden for providing the theoretical calculations as well as the useful
%discussions we had on this topic. This work was supported in part by the U.S. Department of Energy (DOE), Office of Science, Office of Nuclear Physics
%under grant No. DE-SC0013620 and contract DE-AC05-06OR23177, the Nuclear Regulatory Commission (NRC) Fellowship
%under grant No. NRC-HQ-84-14-G-0040, the Doctoral Evidence Acquisition (DEA) Fellowship and the Natural Sciences and Engineering Research Council of Canada (NSERC).

%---include references that are not mentioned in the main text
%---but are included in the supplemental material
%---cite supp. material as follows:  (See Supplemental Material) after description of the topic being discussed.
%\nocite{COSY}
\end{document}
\bibliography{ms}
%\end{document}

### 2020-10-03 PRL_UTILITIES_CODES/supplementary_materials/latex_files/supp.tex
finalized supp. materials and modifications of prl text / images

acceptance model\cite{COSY} using the simulation program, SIMC. The proton form factor parametrization of Ref.\cite{PhysRevC.69.022201} were used. \\

@@

tangent to the spectrometer central axis ($+z$) and are defined as $Y'_{\mathrm{tar}} = \frac{dY_{\mathrm{tar}}}{dz}$ and $X'_{\mathrm{tar}} = \frac{dX_{\mathrm{tar}}}{dz}$.

@@

  and the data-to-SIMC ratio numerical values (top-left). The bottom panel shows the ratio of the data (Y$_{\mathrm{data}}$) to SIMC (Y$_{\mathrm{SIMC}}$) on a bin-by-bin basis, where the inner (black)
and outer (blue) dashed lines represent a percent deviation from unity of $\pm10\%$ and $\pm20\%$, respectively.}

@@

  Inset (left): The SHMS momentum fraction was set by the HMS $\delta$ cut to be $\lesssim$3$\%$ which is well within the SHMS specifications of  $-10 \leq \delta \leq22 \%$}

@@

\caption{Event selection cuts on the $ep$ coincidence time (left) and total deposited energy on calorimeted normalized by the track momentum (right).}

@@

\caption{Geometrical acceptance cut on reconstructed events projected at the HMS collimator (left). The SHMS events (in coincidence with HMS events) were projected at the SHMS collimator (right)
  which clearly shows that the acceptance of the SHMS is driven by that of the HMS.}

@@

\noindent The radiative corrections were applied by multiplying the ratio of non-radiative to radiative SIMC yields to the data yield for each ($\theta_{nq}$,$p_{\mathrm{r}}$)

@@

The bin centering corrections were applied by multiplying the ratio, $f_{bc} \equiv \sigma_{avg.kin}/\bar{\sigma}$, to the average data cross section over each ($\theta_{nq}$,$p_{\mathrm{r}}$)

@@

cuts can be found in Section 5.10 of Ref. \cite{cyero_phdthesis}. 

@@

the model dependency on the correction factors have a negligible effect on the experimental cross sections.

@@

>>>>

acceptance model\cite{COSY} using the simulation program, SIMC. The proton form factor parametrization of Ref.\cite{PhysRevC.69.022201} was used. \\

@@

tangent to the spectrometer central optics axis ($+z$) and are defined as $Y'_{\mathrm{tar}} = \frac{dY_{\mathrm{tar}}}{dz}$ and $X'_{\mathrm{tar}} = \frac{dX_{\mathrm{tar}}}{dz}$.

@@

  and the data-to-SIMC ratio numerical values (top-left corner). The bottom panel shows the data to SIMC yield ratio (Y$_{\mathrm{data}}$/Y$_{\mathrm{SIMC}}$) on a
  bin-by-bin basis, where the inner (black) and outer (blue) dashed lines represent a percent deviation from unity of $\pm10\%$ and $\pm20\%$, respectively.}

@@

  Inset (left): The SHMS momentum fraction was set by the HMS $\delta$ cut to be $\lesssim$3$\%$ which is well within the SHMS momentum acceptance range of $-10 \leq \delta \leq22 \%$}

@@

\caption{Event selection cuts on the electron-proton ($ep$) coincidence time (left) and total deposited energy on calorimeted normalized by the particle track momentum (right).}

@@

\caption{(left) Geometrical acceptance cut on reconstructed events projected at the HMS collimator. (right) The SHMS events (correlated with HMS events on left plot), projected at the SHMS collimator.
  The projection at the SHMS collimator clearly shows that the acceptance of the SHMS is driven by that of the HMS.}

@@

\noindent The radiative corrections were applied by multiplying the ratio of non-radiative to radiative SIMC yields to the data yield for each ($\theta_{nq}$, $p_{\mathrm{r}}$)

@@

The bin centering corrections were applied by multiplying the ratio, $f_{\mathrm{bc}} \equiv \sigma_{\mathrm{avg.kin}}/\bar{\sigma}$, to the average data cross section over each ($\theta_{nq}$, $p_{\mathrm{r}}$)

@@

cuts systematics can be found in Section 5.10 of Ref. \cite{cyero_phdthesis}. 

@@

the model dependency of the correction factors have a negligible effect on the experimental cross sections.

@@

%\clearpage
